### 2019-01-16 thesis_report/methods.tex
updated methods

	\subsection{Eliminating long trajectories}
		\comment{We devise two different ways to define the cutoff of momentum.}

@@

		\subsubsection{Momentum cutoff}
			We take the longest trajectory possible in a zigzag segment
		\subsubsection{Angular cutoff}

>>>>

	\subsection{Eliminating long trajectories}

@@

		\comment{We make an analogy between the cutoff of long trajectories to the cutoff of high momenta.}
		We hypothesize that the increase of the topological gap in a zigzag is due to the cutoff of long trajectories.
		In order to make substantiate that this is indeed the driving mechanism behind the improvement, we propose an analogy using the bandstructure of a regular SNS junction.

		\comment{We map the zigzag to an infinite SNS junction with tilted magnetic field and a range of forbidden momenta.}
		We essentially take a single diagonal section of a zigzag, and map it to a normal, infinite SNS junction.
		The new coordinate system is depicted by the set of axes with $x^\prime$ and $y^\prime$ in Fig.~\ref{fig:setup}.
		Note that the magnetic field has an angle $\theta$ with respect to the $x^\prime$ axis.
		We identify trajectories cut off by the zigzag with a particular range of forbidden momenta.
		By then analysing the bandstructure of this infinite SNS junction, ignoring the forbidden momenta, we can give an estimate the resulting gap of the device.
		As the system is only momentum localized in the $x$ direction (the translationally invariant direction), we only control $\kx$.
		Denoting the set of allowed momenta by $\Omega$, the equation for the estimated topological gap becomes,

		\begin{equation}
			\Delta_\text{topological} = \min_{\kx\in\Omega} \left\rvert E(\kx) \right\rvert
			\label{eq:definition_gap}
		\end{equation}

		\comment{We first link the long trajectories to a maximum allowed angle.}
		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$$ axis.
		By defining a minimum angle, we thus can filter out the long trajectories.
		We define this angle by identifying the angle

		\subsubsection{Momentum cutoff}
			\comment{We link the allowed angle by estimating it by $k_x = k_F \cos(\alpha)$}
			We take the longest trajectory possible in a zigzag segment

		\subsubsection{Angular cutoff}
            \begin{equation}
            \sin (\alpha_\text{max}) = \frac{v_y}{v_x} = \frac{ \frac{\de E}{\de k_y} }{ \frac{\de E}{\de k_x} }
            \end{equation}
